KV Analysis for Non-Expressive performances

### 2020-05-12 material/analysis/stim_n/analysis/duration.Rmd
add # of excluded participants / modify layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of non-expressive performance (duration) from teaching-v2.0.

@@

# Duration
## 1. All - individual
- Average normDu for each participant.

@@

## 2. All - group

@@

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```

# Duration Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

@@

### Exclude outlier performacnes
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```

>>>>

Description: This is a rough overview of non-expressive performance (Duration) from teaching-v2.0.

@@

# Duration
## 1. All - individual
- Average normDu for each participant

@@

## 2. All - group
- Average normDu

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

# Duration Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

@@

## 2. All - group
- Average CV

```{r cv_all, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
```

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2020-05-12 material/analysis/stim_n/analysis/ioi_offset.Rmd
change file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
add # of excluded participants / modify layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOI-Offset Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

# IOI
## 1. All - individual
- Average normIOIs for each participant.

@@

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

@@

### Exclude outlier performances
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```

>>>>

---
title: 'IOI-Offset Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
dt_ioi <- fread("../preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

# IOI
## 1. All - individual
- Average normIOIs for each participant

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

# IOI Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

@@

## 2. All - group
- Average CV

```{r cv_all, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
```

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2020-05-12 material/analysis/stim_n/analysis/ioi_onset.Rmd
change file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
add # of excluded participants / modify layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

### Exclude outlier performances
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```

>>>>

```{r extract, include = FALSE}
dt_ioi <- fread("../preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

# IOI Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
## 2. All - group
- Average CV

```{r cv_all, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
```

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2020-05-12 material/analysis/stim_n/analysis/kv.Rmd
change file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
add # of excluded participants / modify layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'KV Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
_
Description: This is a rough overview of non-expressive performance (KV) from teaching-v2.0.

@@

```{r extract, include = FALSE}
dt_kv <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```

# KV Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr, TrialNr)]
cv
```

>>>>

---
title: 'KV Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance (KV) from teaching-v2.0.

@@

```{r extract, include = FALSE}
dt_kv <- fread("../preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r kv_all$N-nrow(excluded_kv)`

# KV Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr, TrialNr)]
cv
```
